---
title: "Introduction to strop"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to strop}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(strop)
```

# General bootstrap functionality

At the core of `strop` is the `bootstrap` function. This is a generic function with a default method (for one-dimensional data) and a method for data frames (two-dimensional data). This function is a constructor for an object of class `strop`, which can be used in the package's other provided functions.

## Single-valued bootstrap

Single-valued bootstrapping is straightforward: the default function used by `bootstrap` is `mean`.

```{r}
data(mtcars)
bootstrap(mtcars$hp)$pop
```

## Multivalued bootstrap

Both the data frame and default constructors may be used with multivalued functions.

```{r}
cen <- function(x) list(mean = mean(x), median = median(x))
bootstrap(mtcars$hp, cen)$pop
```

## Calculating bootstrap quantiles

`strop` provides a `quantile.strop` function for calculating quantiles based on the bootstrap procedure. This function simply delegates to `quantile(obj$stats)`.

```{r}
quantile(bootstrap(mtcars$hp), c(0.05, 0.95))
```

## Calculating bootstrap confidence intervals

`strop` exposes a `confint.strop` function for calculating central confidence intervals based on the bootstrap procedure.

```{r}
confint(bootstrap(mtcars$hp, n = 100))
```

## Printing bootstrap results

`strop` provides a `print.strop` function for assessing the results of bootstrap iteration. The function call, (original) sample estimates, and the beginning of the list of bootstrap estimates are printed.

```{r}
print(bootstrap(mtcars$hp, n = 100))
```

## Visualizing bootstrap results

`strop` provides `plot.strop` function to visualize the results of a bootstrap application. A histogram of each statistic is plotted for multi-valued bootstrapping, and central confidence intervals are indicated on each plot.

```{r}
plot(bootstrap(mtcars$hp, n = 100))
```

# Multiple linear regression

`strop` provides a convenience function for multiple linear regression analysis using the bootstrap procedure: `mlrboot`. Given a fitted model object, `mlrboot` produces a bootstrap object for the estimation of model coefficients.

```{r}
fit <- lm(hp ~ ., data = mtcars)
boot <- mlrboot(fit)
print(boot, max = 5)
plot(boot, vars = c("cyl", "wt"))
```
